---
title: "Data structures"
---
An overview of R data structures.

# Vectors
```{r}
my_vec <- c(1, 2, 3, 4) # Can contain other data types, but must all be the same type. E.g. All boolean, or all character.
my_vec
```

## Indexing vectors
```{r}
my_vec[1]
my_vec[1:3]
my_vec[1:length(my_vec)]
my_vec[c(1,3,4)] # Select specific indicies
```

## Assigning names
```{r}
names(my_vec) <- c('head_1', 'head_2', 'head_3', 'head_4')
my_vec
my_vec['head_1']
```

# Data frames
```{r}
my_df <- data.frame(col1=c(1,2,2), col2=c(3,4,4), col3=c(5,6,6)) # df columns created from vectors
my_df
```

## Indexing dfs
```{r}
my_df$col1
my_df[1:2, 'col1']
my_df[1:nrow(my_df), c('col1','col3')]

subset(my_df, col2>3) # Select rows based on condition
```

# Lists
List items can have different data types, shapes and lengths.
```{r}
my_list <- list(item1=my_vec, item2=my_df)
my_list
```

## Indexing lists
Various ways to select all elements in first item of the list:
```{r}
my_list[[1]] # Or my_list[['item1']], or my_list$item1
```
Select elements within list items:
```{r}
my_list[[2]][1]
my_list[[2]]$col1
my_list[[2]][1:2, 'col1'] # etc
```

# Determing data type
Various functions to determine the type of a varaible or an object.
```{r}
class(my_vec) # Data type of data within object
str(my_vec)
typeof(my_vec)
is.vector(my_vec)

```